\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate estimates of luminosity and distance\\ for luminous red-giant stars }

### 2018-08-01 paper/sp.tex
ACE inputs

% To-do items
% -----------
% - draft introduction
% - draft discussion
% - make sure we address the sensibleness and generality of the linear model for the photometric space
% - address the non-convexity of the model (see twitter convo with @andy_l_jones).
% - Coryn's point that we should carefully explain how our model is geometric.
% - related: HWR's point that this is standardizeable candles, like the Ia SNe results.
% - related: Put in an explanation of WHY this works so well.
% - related: Put in an explanation of how it is that we aren't really modeling luminosity or distance but really just generating parallaxes.
% - does the model need a cute name, like The Swan?
% - we need a Facilities list / tags
% - we need a Software list / tags

@@

From the \apogee\ data on these low-$\logg$ stars, we take the spectral pixels,
of which there are ACE HOW MANY, on a common rest-frame wavelength grid.
That is, every \apogee\ star is extracted on (or interpolated to)
the same wavelength scale.
In detail, we obtain the
the \apogee\ spectral pixels from the pipeline-generated \code{ACE whatever} files.
We then pseudo-continuum-normalize the spectra according to the procedure developed
in \project{The~Cannon} (HOGG CITE): That is, the pseudo-continuum is a spline fit to a set
of pixels chosen to be insensitive to stellar parameters.
We use as our spectral data the normalized spectral pixel values.

@@

ACE: We match the \apogee+\zmass\ stars to he \wise\ ACE WHICH CATALOG by ACE WHAT CRITERION?
This gives, fore each matching star $n$,
mid-infrared photometry $W_{1n}$ and $W_{2n}$ at 3.6 and 4.5\,$\mu$m
In detail we use the ACE WHAT SPECIFIC CATALOG ENTRIES?

We match this full-match catalog to the \gaia\ \acronym{DR2} (HOGG CITE) by what criteria?

We take from the \gaia\ \acronym{DR2} Catalog the photometric data
$G_n$ (\code{phot_g_mean_mag}),
${BP}_n$ (\code{phot_bp_mean_mag}),
and ${RP})_n$ (\code{phot_rp_mean_mag}),
which will become part of the feature vector $x_n$.
We do not use the entire \gaia\ \acronym{DR2} Catalog but instead the subset
that meets ACE WHAT ADDITIONAL PHOTOMETRIC CUTS?

>>>>

% To-do items
% -----------
% - draft introduction
% - draft discussion
% - make sure we address the sensibleness and generality of the linear model for the photometric space
% - address the non-convexity of the model (see twitter convo with @andy_l_jones).
% - Coryn's point that we should carefully explain how our model is geometric.
% - related: HWR's point that this is standardizeable candles, like the Ia SNe results.
% - related: Put in an explanation of WHY this works so well.
% - related: Put in an explanation of how it is that we aren't really modeling luminosity or distance but really just generating parallaxes.
% - does the model need a cute name, like The Swan?
% - we need a Facilities list / tags
% - we need a Software list / tags
% - check with WISE experts that we have the correct WISE photometry

@@

From the \apogee\ data on these low-$\logg$ stars, we take the spectral pixels,
of which there are 7405 (after cutting out pixels that rarely or never get data),
on a common rest-frame wavelength grid.
That is, every \apogee\ star is extracted on (or interpolated to)
the same wavelength scale.
In detail, we obtain the
the \apogee\ spectral pixels from the pipeline-generated \code{aspcapStar} files.
We then pseudo-continuum-normalize the spectra according to the procedure developed
in \project{The~Cannon} (HOGG CITE):
That is, the pseudo-continuum is a spline fit to a set
of pixels chosen to be insensitive to stellar parameters.
We use as our spectral data the normalized spectral pixel values.

@@

We used the \gaia\ Archive (HOGG CITE) to match the \apogee+\zmass\ stars
to the \wise\ Catalog (HOGG CITE),
according to the \gaia\ Archive internal match criteria.
This gives, fore each matching star $n$,
mid-infrared photometry $W_{1n}$ and $W_{2n}$ at 3.6 and 4.5\,$\mu$m
In detail we use the \code{w1mpro} and \code{w2mpro} Catalog entries.

We match this full-match catalog to the \gaia\ \acronym{DR2} (HOGG CITE)
using the \gaia\ Archive official match (given the \zmass\ IDs).
We take from the \gaia\ \acronym{DR2} Catalog the photometric data
$G_n$ (\code{phot_g_mean_mag}),
${BP}_n$ (\code{phot_bp_mean_mag}),
and ${RP}_n$ (\code{phot_rp_mean_mag}),
which will become part of the feature vector $x_n$.
